%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2020} 
\acmYear{2020} 
\setcopyright{acmcopyright}
\acmConference[CEP 2020]{Computing Education Practice 2020}{January 9, 2020}{Durham, United Kingdom}
%\acmBooktitle{Computing Education Practice 2020 (CEP 2020), January 9, 2020, Durham, United Kingdom}
\acmPrice{15.00}
\acmDOI{10.1145/3372356.3372362}
\acmISBN{978-1-4503-7729-4/20/01}

%\usepackage{dirtytalk}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title[UK Computer Science Degree Accreditation,
Post-Shadbolt]{Computer Science Degree Accreditation in the UK:\\A
Post-Shadbolt Review Update}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Tom Crick}
\orcid{0000-0001-5196-9389}
\affiliation{%
\institution{Swansea University}
\city{Swansea}
\country{UK}
 }
\email{thomas.crick@swansea.ac.uk}

\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
\institution{ University of Bath}
\city{Bath}
\country{UK}
}
\email{j.h.davenport@bath.ac.uk}

\author{Paul Hanna}
\affiliation{%
\institution{Ulster University}
\city{Belfast}
\country{UK}
}
\email{jrp.hanna@ulster.ac.uk}

\author{Alastair Irons}
\affiliation{%
\institution{ Sunderland University}
 \city{Sunderland}
\country{UK}
}
\email{alastair.irons@sunderland.ac.uk}

\author{Tom Prickett}
\affiliation{%
 \institution{ Northumbria University}
 \city{Newcastle upon Tyne}
 \country{UK}
 }
\email{tom.prickett@northumbria.ac.uk}


%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Crick, Davenport, Hanna, Irons, and Prickett}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
The assurance of quality through degree accreditation by Professional,
Statutory and Regulatory Bodies (PSRBs) is very much a feature of
higher education in the UK.  In this dynamic and emerging UK
educational, economic and policy environment, there still remains a
need for accreditation regimes to evolve in order to maximise the
value they provide to higher education institutions, as well as to
industry and society as a whole.

The Shadbolt review, an independent review of computer science degree
accreditation and graduate employability conducted in 2016, focused on
the purpose and role of degree accreditation, how the system can
support the skills requirements of employers, and how the system can
improve graduate employability. This paper provides an update in the
context of one professional body -- BCS, The Chartered Institute for
IT -- of what has happened in response to the recommendations of the
Shadbolt review, focusing on ongoing enhancement projects, as well as
commentary and recommendations for future activities and initiatives.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003456.10003457.10003527.10003529</concept_id>
<concept_desc>Social and professional topics~Accreditation</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003527.10003531</concept_id>
<concept_desc>Social and professional topics~Computing education programs</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003580.10003568</concept_id>
<concept_desc>Social and professional topics~Employment issues</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Social and professional topics~Accreditation}
\ccsdesc[300]{Social and professional topics~Computing education programs}
\ccsdesc[100]{Social and professional topics~Employment issues}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Accreditation, PSRB, Curricula Design}


%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

%A short description of the practice you're presenting
\section {What is it?}

The Shadbolt Review~\cite{shadbolt2016shadbolt}, published in May
2016, investigated the relatively high unemployment rates graduates of
computer science and related degrees in the UK and the role of degree
accreditation in promoting employability. The Shadbolt review noted
that the disparity in `raw' unemployment rates was largely accounted
for by prior achievement and socio-economic factors, and that rates of
graduate unemployment were declining and varied considerably between
geographic location and type of higher education institution
(HEI). The discipline was already acting proactively to address the
issue.  Related professional bodies have enhanced their accreditation
processes in response these challenges. BCS has made significant
adjustments to their accreditation processes since 2015; these were
partly in response to the discussions related to and the
recommendations of Shadbolt but also to other changes in the sector
and the discipline.  These have been communicated to the assessor
community and to those responsible for leading the development of HEI
accreditation applications. However, there are many academics who are
less intimately involved in accreditation: this paper serves to
communicate these and future enhancements to them and the wider
computer science education community.

%What happened before? What is it changing / replacing / improving? What gap is it filling?
\section {Why are you doing it?}	

The Shadbolt review~\cite[p.~8]{shadbolt2016shadbolt} makes two main
recommendations for the enhancement of accreditation regimes, one
related to the {\emph{Academic Accreditation of Degree Courses}} and
the other related to {\emph{Engaging Industry in
Accreditation}}. Criticism of the accreditation of degree programmes
is not new. There is a history of claiming the processes are
unnecessarily bureaucratic and constrain innovation \cite{Harvey2004},
and there are dangers of accreditation streams being revenues streams
in their own right rather than for the benefit of a discipline or
wider society \cite{Knight_2015}. Equally its value has been
highlighted particularly in the context of a potentially globally
mobile workforce \cite{Knight_2015}. Hence, the challenge set for BCS
and other accreditation providers that operate in the Computer Science
discipline is broadly to: increase awareness and value of
accreditation; focus upon outputs; maintain internationally recognised
standards; respond to emerging technology trends and developments;
promote enhancement and innovation; engage industry; and reduce the
perceived bureaucracy involved.

% \begin{comment}

% %%\begin{quote} 
% 	"Recommendation 9 - Academic Accreditation of Degree Courses.
	
% 	BCS, IET and Tech Partnership should ensure that existing systems of degree course
% 	accreditation are flexible, agile, and enable HE providers to respond to changing
% 	demand and emerging technological trends and developments. Accreditation of courses
% 	should be focused on outputs. Accrediting bodies should work to increase awareness
% 	and value of accreditation so that it is valued by HE providers, students and employers,
% 	and consider how their role can provide a forum for engagement between HE and
% 	employers.

% 	Recommendation 10 - Engaging industry in accreditation.

% 	Employers, through employer groups, such as Tech Partnership, should engage more
% 	consistently with HE providers and BCS \& IET to ensure accreditation is effective and
% 	reflects current industry demand."
% %%\end{quote}
% \end{comment} 


\section {Where does it fit?}
%A short description of your teaching context. You may, for instance, include a description of intake, class size, curriculum sequence; anything that's necessary for others to understand your situation. How do things work at your institution?

In the UK, the most common form of accreditation for computer science
and cognate disciplines is through two professional bodies: BCS, The
Chartered Institute for IT (BCS) and the Institution of Engineering
and Technology (IET). The accreditation provided by these bodies are
underpinned by international initiatives such as the Washington
Accord~\cite[for CEng]{Washington2019} and Seoul Accord~\cite[for
CITP]{Seoul2019}. These memoranda support the internationalising of
the curriculum and promote consistency and parity in computer science
education globally. The BCS and IET broadly check two
things~\cite{BCS2018a, IET2019}:
    {\emph{
\begin{enumerate}
    %\item Is the quality of experience provided by a HEI appropriate for accreditation?
    \item Are the exit standards of the programme appropriate for the
level of accreditation sought?  A number of standards are considered
including entry, progression, retention, awards and graduate
employability.  This is supplemented by other evidence of the quality
of the provision, for example external examiners reports, the most
recent subject review, annual review information, evidence of employer
involvement, linkage with research. Together this evidences that a
programme is of an appropriate quality to support accreditation.
    \item Are the curricula exit standards of a programme consistent
with the learning outcomes expected for the accreditation sought? The
expected exit standards should conform with the international
memorandum (Washington or Seoul Accord or both).
\end{enumerate}}}

%BCS is addressing the recommendations of the Shadbolt Review in the following ways.

\subsection{The value of accreditation}

What is the value of an accredited degree? Like all forms of
accreditation/endorsement, it provides a recognised kitemark that can
assist marketing and promotion of programmes. Whilst a standards-based
approach is followed, an enhancement-focused approach is increasingly
taken; in addition, the BCS is continuing a conversation to explore
the value proposition of accreditation from the point of view of other
stakeholders. The following are aspects of the value to accredited
HEIs.

%\subsubsection{Maintaining standards}
{\textbf{Raising output standards}}
% \begin{comment}
% version 1
% BCS refuses accreditation for programmes that do not meet the expected output standards or when achievement of the curricula exit standards for the accreditation sought are not met. "\% of graduates in related professional 6 months after graduating" \cite[p8]{BCS2019b} is the employability output standard applied to each programme. Departments are also requested to  "A 1.1.6 Describe how employability skills are developed within the students and how students are supported in their professional development" \cite [p3]{BCS2019b}. Both these criteria were introduced in response to Shadbolt.
% \end{comment}
% \begin{comment}
% version 2
% BCS refuses accreditation for programmes that do not meet the expected output standards. "\% of graduates in related professional 6 months after graduating" \cite[p8]{BCS2019b} is the employability output standard applied to each programme. Departments are also requested to  "A 1.1.6 Describe how employability skills are developed within the students and how students are supported in their professional development" \cite [p3]{BCS2019b}. Both these criteria were introduced in response to Shadbolt.
% \end{comment}
BCS can and has refused accreditation for programmes that are not of
an appropriate quality for accreditation. However, an
enhancement-focused rather than prescriptive approach is now adopted;
quality is considered on a holistic basis. In response to the Shadbolt
review, two criteria were introduced: ``{\emph{\% of graduates in
related professional employment 6 months after graduating}}''~\cite
[p8]{BCS2019b} and ``{\emph{Describe how employability skills are
developed within the students and how students are supported in their
professional development}}''~\cite [p3]{BCS2019b}.

% BCS refuses accreditation when achievement of the curricula exit
% standards for the accreditation sought are not met.
{\textbf{Promoting internationally-recognised standards}} The BCS
accredits to internationally-recognised standards, which evidence the
global parity of the degree programmes accredited. Part of the value
here is linked to the value of professional registration; this assists
in the global mobility for the graduates of accredited programmes. BCS
currently has a project investigating how to enhance the value of
professional registration to students, graduates and early career
professionals.

{\textbf{Ensuring curricula relevance}} With the agreement of the
sector, normally reached through the Council of Professors and Heads
of Computing (CPHC), it is possible to agree and promote curricula
change. The most recent example of this is the inclusion of
cybersecurity in all accredited degrees~\cite{Cricketal2019}. BCS
mandates the inclusion of security in all accredited degree programmes
to a standard agreed between professional bodies, industry and
government. BCS had been requiring coverage since 2015
\cite[p.~17--18]{BCS2018a} with the result that all accredited
universities must be compliant by 2020 (due to the five-year cycle of
accreditation) \cite{Cricketal2019}. Furthermore, group working
experience is mandated by BCS (criterion 2.3.1~\cite [p31]
{BCS2018a}). This is extremely valued by employers, but typically
disliked by students at the time, and features negatively in many
student surveys. It is likely that if many UK universities, which are
heavily judged by current student opinion, were left to themselves
without accreditation, they would probably remove group working.

% This year's Royal Institution Christmas lecture considers ethical
% questions related to computing and mathematics
% \cite{RoyalInstitution2019}. This is a curricula element that has been
% mandated by BCS accreditation in the form of legal, social, ethical
% and professional issues for a number of years \cite{Brooke2018}.

{\textbf{Disseminating good practice}} BCS accreditation panels have
been identifying aspects of good practice for wider dissemination for
a number of years. Since 2016, the process has been refined to more
clearly signpost commendations. BCS is currently in the process of
refining the promotion of good practice. One short term initiative,
from autumn 2019, visited HEIs will be offered the opportunity to
showcase an aspect of their provision or practice. The intention is to
generate further good practice examples that a visiting panel can
potentially commend.

{\textbf{Industry relevance}} All BCS accreditation panels include an
industrial assessor whose role includes ensuring that programmes are
providing quality and currency, to develop graduates who are able to
enter a competitive employment market. Evidence that a visited HEI's
mechanisms for engaging with industry are supporting graduates so as
to achieve the expected exit standards are sought from a variety of
sources, including the curricula studied; the assessments and
examinations sat; and the engagement mechanisms themselves.

% remove this section if needed?
% {\textbf{Independent peer review}} Peer review is commonly used in
% quality regimes in higher education and in periodic review
% processes; in most cases the HEI being reviewed chooses the peer. As
% part of a BCS (or other professional body) accreditation, an HEI has
% less choice regarding who completes a review and hence such a review
% is arguably more independent. BCS review panels contain a
% minimum of two experienced assessors who have strong awareness of the
% discipline norms across the UK sector.

%\subsection{Accrediting work experience}

{\textbf{Accrediting work experience}} BCS has introduced
accreditation to Professional Registration for IT Technicians
(RITTech) as a mechanism for accrediting industrial experience (or
work-based learning) gained during a placement, foundation degree or
work-experience as part of a degree apprenticeship
\cite[p8]{BCS2018a}. This development was introduced in response to
the Shadbolt review.

\subsection{Driving improvement}

The Shadbolt report has led to a number of enhancements, with a
variety of sources of data being employed to help drive the improvement
efforts. For example, the BCS Secretariat continually evaluate via the
use of opinion surveys and informal conversations. Views are gathered
related to briefing sessions, pre-visit communications and visits;
following a visit BCS panels engage in peer review. The feedback
gained from these sources is explored and opportunities for
enhancement agreed at accreditation committee meetings. Prioritised
working groups then complete the enhancement projects.

\subsection{Reducing bureaucracy}

Continuous review of BCS Accreditation practice has been taking place
since 2015 with the intention of adopting an enhancement-focused
agenda; reducing the amount of bespoke documentation that is required;
using technology to assist the process, whilst enforcing the
international standards. Working through the process from an HEI
prospective has resulted in the following changes:

{\textbf{HEIs briefing}} For a number of years all visited HEIs have
been encouraged to attend a briefing to explore the BCS requirements
with a focus upon any changes since the last visit and common
challenges. Attendance has understandably been mixed, partly due to
travel and funding. Since 201, all briefings have taken place by video
conference; feedback on this approach has been positive.

{\textbf{The application itself}} From a paper+digital submission
before 2015, BCS has now moved to a fully digital submission. BCS is
flexible in how the information is submitted, including the use of
institutional virtual learning environments. Most of the application
consists of an evidence base which HEIs will already have. This is
supplemented by a summary of the provision and each programme in which
the department are welcome to reference existing resources. HEIs are
still required to provide a mapping of where the BCS requirements are
taught and assessed within each programme; this is required to
evidence where the accreditation-specific requirements (such as
security or ethics) are met in a particular programme.

{\textbf{Areas for discussion at visits}} It is now normal practice
for a BCS panel to communicate likely areas of discussion to the HEI
prior to the visit wherever possible (but HEI applications may be late
or other issues can emerge as part of the visit).  This has resulted
in discussions tending to become more collegiate, supportive and
constructive.

% \begin{comment}
% \subsection{Promoting the value of accreditation}
% The value proposition discussed in this document is a definition of the value of accreditation from those who are intimately involved. BCS is in the process of initiating a conversation to explore the value proposition of accreditation from the point of view of other stakeholders.
% \end{comment}

% how do you know? Give some evidence of effectiveness in context.
\section {Does it work?}

HEIs choose which programmes are submitted or not in an accreditation
application; as such, only a sample of provision may be
considered. However, a proxy for success is the anonymous feedback BCS
obtains post-visit. Some key aspects of this feedback are shown in
Table 1~\ref{table:1}; overall the results are positive, indicating
the process is generally valued and shows the increased attendance of
the virtual briefing over the physical one.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
%\begin{table}[]
\begin{table}[h!]
  \caption{Selected results from accreditation visit feedback survey}
  \label{table:1}
%\resizebox{\textwidth}{!}{%
%\begin{tabular}{lllll}
\begin{tabular}{ | p{5cm}|p{.75cm}|p{.75cm} |p{.75cm} |}
\hline
 & 2017 & 2018 & 2019   \\ \hline
Responses & 12 & 14 & 16   \\
\hline
Attended pre-visit briefing & 6 & 14 & 16   \\
\hline
The visit felt to be worthwhile: & & &  \\
Strongly Agree &92\% & 93\% &88\% \\
Agree &0\% & 7\% &0\% \\
Tend to Agree &0\% & 0\% &6\% \\
Strongly Disagree &8\% & 0\% &0\% \\
No reply &0\% & 0\% &6\% \\
\hline
Overall how satisfied with the visit? & & &  \\
Very Satisfied &83\% & 86\% &94\% \\
Quite Satisfied &8\% & 14\% &6\% \\
Not Satisfied at all &8\% & 0\% &0\% \\
\hline

\end{tabular}%
%}
\end{table}

Recent work indicates that accreditation has driven cybersecurity
education in the UK~\cite{Cricketal2019} -- as opposed to the US,
where is it also in the recommended curricula -- but the
corresponding accreditation requirements are much more recent.

%Where did you get the idea from? (If from published reports, please include references). How did you find out about it? Was it easy/hard to adopt? What did you change?
\section {Who else has done this?}	

In the UK for the broad computing area, in addition to IET and BCS
providing accreditation, a number of agencies provide
endorsement. These schemes are commonly intended to promote
employability of graduates. This bodies include Tech Partnership
Degrees ~\cite{TP2019}; TIGA a trade association representing the UK's
games industry and Screenskills (formerly Creative Skillset)
\cite{Screenskills2019}; The Chartered Society of Forensic Sciences
\cite{CSOFS2019}; and the National Cyber Security Centre (NCSC)
\cite{NCSC2018a}. There is little published regarding the
effectiveness or otherwise of these endorsements.

\begin{comment}

In addition to IET and BCS, accreditation in the broad computing area in the UK is also being performed by a few different agencies. A number of bodies are providing endorsements intended to promote employability. Tech Partnership Degrees provides endorsements to Higher Education programmes with specific curricula elements aimed at job market requirements \cite{TP2019}. Tech Partnership Degrees have a specialist scope, endorsing programmes in the area of IT Management for Business and Software Engineering for Business. For games related degrees, TIGA a trade association representing the UK's games industry and  Screenskills (formerly Creative Skillset) \cite{Screenskills2019} operate a similar role. For digital forensics The Chartered Society of Forensic Sciences \cite{CSOFS2019} provides industry related endorsements.  National Cyber Security Centre (NCSC) is a UK Government organisation tasked with enhancing the cybersecurity of the UK and accredits programmes with significant cybersecurity content \cite{NCSC2018a}. There is little published regarding the effectiveness or otherwise of these endorsements.

\end{comment}

The Institute of Coding (IoC) is a not for profit organisation that intends to enhance how Digital Skills are developed in Higher Education in the UK \cite{Davenportetal2019a}. A micro-credentialing approach is being taken to its proposed accreditation regime. This could potentially augment the current recognised pathways to professional accreditation by providing a more fine-grained alternatives that could be useful to some employers or employees who wish to evidence their achievements in an accredited manner.  One of the challenges in this work is the lack of an agreed standard (in the way there is for the Seoul and Washington Accords) for micro-credentialing. This approach is also looking at work experience with the aspiration to accredit student competences in work related skills. The BCS is actively working with IoC and intends to collaborate with the IoC in any initiatives of mutual benefit.

The wider Computer Science discipline has also responded actively to the challenges presented by Shadbolt with CPHC operating four working groups \cite{cphc_2016}.  The Royal Academy of Engineering Visiting Industrial Professor Scheme \cite{royal} has promoted further engagement between industry and academia.

\section {What will you do next?}	
%Will you vary this, or develop it further?
As discussed earlier, BCS has initiated a conversation to explore the
value-proposition of accreditation from other stakeholders points of
view. The BCS is also exploring the value-proposition BCS professional
membership
represents to students, graduates and early career professionals. As
indicated previously an industrial assessor is a critical part of
every visit panel. There are also interesting developments being led
by the IoC related to micro-credentialing. BCS will continue to
consider opportunities for the further involvement of employers in
accreditation. BCS is currently in the process of refining its
processes for the promotion of good practice. In addition to these
enhancements, there are number of enhancements either in progress or
planned for the future which are considered next.

%\subsection{Internationalization}
BCS accreditation primarily takes place in the UK, however there are a small but growing number of institutions outside the UK that BCS accredits. Under the terms of the Washington and Seoul Accords, BCS does not engage in accreditation in the jurisdictions of Accord signatories without first consulting with the related local professional body.  On occasions BCS guidelines employ English / Welsh higher education terms without indicating that local equivalents are equally acceptable. The next set of guidelines will address this shortcoming.

%\subsection {Engineering Council and Accreditation of Higher Education Programmes (AHEP) Version 4}
In the British jurisdiction of the Washington accord, the approach adopted is unusual in that the Engineering Council extends the license to accredit \emph{Chartered Engineer} to a large number of professional bodies \cite{EC2019}. This is not the practice adopted in other jurisdictions, for example in the United States of America ABET is the sole body. A recent audit by the Washington Accord has highlighted divergence in practice in some areas with respect to Chartered Engineer Accreditation. The Engineering Council is in the process of seeking further consistency. This has led to the new rules with respect of Compensation and Condonement for Eng accreditation \cite{EC2018}. Further changes are embedded in Accreditation of Higher Education Programmes version 4 (AHEP 4). The BCS requirements have been updated to reflect the expectations of Compensation and Condonement. Once AHEP 4 is finalised further work will be required to address these updates. Among other proposals, AHEP 4 intends to extend Chartered Engineering accreditation to include diversity and widening participation data (of staff and students) as part of the metrics that assess the quality of provision. The Computer Science discipline could clearly do better in this regard, so this should be a positive inclusion.

%\subsection{Agility of processes and changing external environment}
There are considerable external pressures placed upon HEIs, by for example the Research Excellence Framework (REF) and the Teaching Excellence Framework (TEF), which could reduce the priority placed upon accreditation as a mechanism for supporting enhancement. BCS continues to review the bespoke documentation it requires and to make reductions when possible. Care is taken in visit reports to ensure positive aspects of provision are emphasised. This is in part intended to provide evidence that could be used to support future TEF related submissions. Discussions regarding the agility of processes are incorporated into two annualBCS Accreditation Committee meetings to identify enhancements. 

%\subsection {Improve communications and support}
As part of its operation BCS continually reviews and monitors the support process it employs for HEIs seeking accreditation and hence will continue to enhance processes in this area.
There is a strong and vibrant community of academics and industrialists who actively participate in accreditation. However, there are many involved with whom communication could benefit from being more active. A number of initiatives are in process to enhance these communications. For HEIs there are ongoing discussion within BCS regarding establishing a periodic bulletin which could be used to share updates of accreditation practice / procedure, highlight HEIs having their first visit, sharing good practice examples, promote assessor recruitment and so on. Assessor Peer Review has indicated more regular communication with assessors could be of benefit. Virtual link up sessions for assessors are proposed. The BCS are in the process of contacting assessors to determine likely interest and thoughts related to relevant topics for such link ups.

\section{Why are you telling us this?}	
%What is interesting, or useful, about this to someone else?

One of the recommendations of Shadbolt is the value of accreditation
should be more clearly communicated to stakeholders; this paper is
part of a set of initiatives to achieve precisely that.  Much has
changed in BCS accreditation in the last few years; for many academics,
their only experience of BCS accreditation would be their quinquennial BCS
accreditation visit. Accreditation by the BCS is performed by panels
of BCS assessors, and an assessor may be an industrialist or an
academic. The size of a panel varies depending upon the number of
programmes a visited HEI is putting forward for consideration, but a panel
will always include an industrial assessor and two or more academic
assessors. HEIs will have at most two academic assessors from their
staff.  There is a large pool of academic assessors and as such not
all assessors will complete an accreditation visit every
year. Conversely, not all HEIs have an academic assessor; hence a
significant subset of the UK computer science education community are
not informed regarding the evolution of accreditation practice. As
such, the a primary aim of this paper is to share to the wider
community the recent developments, as well as the future enhancement
aspirations and the opportunities to engage in shaping the wider
research and policy agenda in this important area.

\section{Acknowledgments}
The authors wish to thank Sally Pearce, Academic Accreditation Manager
at BCS, The Chartered Institute for IT for supplying the summary
information related to accreditation of UK degree programmes. Many
people, accreditors and accredited, have contributed to accreditation
practice in the UK (and elsewhere), and spreading good practice.  All
authors' institutions are members of the Institute of Coding, an
initiative funded by the Office for Students (England) and the Higher
Education Funding Council for Wales.

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{CEP2020}


\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.
